### 2016-08-09 Docs/managing_jobs/managingjobs.tex
Polish GPU profiling documentation.

\begin{lstlisting}[language=bash,mathescape=false]
$ scorep --cuda --openacc -v ftn program.f90
\end{lstlisting}

@@

After executing, analysis data will be stored in the specified
{\tt SCOREP\_EXPERIMENT\_DIRECTORY}.  With profiling, you
will see a file like profile.cubex.  This can be opened with cube 
(module load cube).

As mentioned, the profiling data can be used to get
recommended settings for tracing.  Running
\begin{lstlisting}[language=bash,mathescape=false]
$ scorep-score -r profile.cubex
\end{lstlisting}
will yield output showing estimated sizes for e.g.~{\tt SCOREP\_TOTAL\_MEMORY}.  It
can also suggest functions to that are called a lot to be filtered out of the
trace.  If you don't care about them and they're slowing scorep down (or making
an outrageously large output file), this is useful to do.

@@

NVIDIA provides tools for specifically analyzing how your code utilizing their
GPUs.  {\tt Score-P} is a fully-featured profiling with some CUDA and OpenACC
support.  It can be useful for providing context for GPU execution and it allows
you to, for example, see line numbers for OpenACC directives that are executed.
{\tt nvprof} will only analyze GPU execution, but in exchange you get much more
detail than is available with {\tt Score-P}.  {\tt nvvp} is NVIDIA's visual
profiler.  It can be used to read data generated by {\tt nvprof}.  Most useful
is the guided analysis it will perform, which analyzes your code's GPU
performance for bottlenecks and suggests ways to improve performance.  Both are
provided when you load the {\tt cudatoolkit} module.

With {\tt nvprof}, no instrumentation is necessary.  Instead, you compile
normally and then run {\tt nvprof} on the executable.  As before, be sure when
executing to load the modules used for compilation.  Executing {\tt nvprof} on
Titan's compute nodes requires some unexpected options having to do with how
{\tt aprun} and {\tt nvprof} interact.

@@

To generate tracing data for {\tt nvvp}, execute
\begin{lstlisting}[language=bash,mathescape=false]
$ aprun -b nvprof --profile-child-processes -o nvprof.timeline.out%p 
  ./gpuprogram.exe arg1 arg2... 
\end{lstlisting}
{\tt nvvp} can then be used to read {\tt nvprof.timeline.out\%p}, where the 
{\tt \%p} will be replaced with the process ID.

>>>>

\begin{lstlisting}[language=bash,mathescape=false]
$ scorep --cuda --openacc -v ftn gpuprogram.f90
\end{lstlisting}

@@

After executing, analysis data will be stored in the specified
{\tt SCOREP\_EXPERIMENT\_DIRECTORY}.  With profiling, you
will see a file like {\tt profile.cubex}.  This can be opened with cube 
({\tt module load cube}).

As mentioned, the profiling data can be used to get recommended settings for
tracing.  Running
\begin{lstlisting}[language=bash,mathescape=false]
$ scorep-score -r profile.cubex
\end{lstlisting}
will yield output showing estimated sizes for e.g.~{\tt SCOREP\_TOTAL\_MEMORY}.
It also list functions that are called many times.  If you don't care about
them and they're slowing {\tt Score-P} down (or making an outrageously large output
file), you can configure {\tt Score-P} to ignore them in its analysis.  To filter a set
of functions, you need to provide a filter file, for example
\begin{lstlisting}[language=bash,mathescape=false]
$ export SCOREP_FILTERING_FILE=scorep.filter
\end{lstlisting}
where
\begin{lstlisting}[language=bash,mathescape=false]
$ cat scorep.filter
SCOREP_REGION_NAMES_BEGIN
 EXCLUDE
   matmul_sub
   matvec_sub
SCOREP_REGION_NAMES_END
\end{lstlisting}
This would tell {\tt Score-P} not to trace the routines {\tt matmul\_sub} and 
{\tt matvec\_sub}.  See the OLCF KnowledgeBase article and/or {\tt Score-P}'s
help for more, but this doesn't seem to be the best-documented aspect of the
program.

@@

NVIDIA provides tools for specifically analyzing how your code utilizes their
GPUs.  {\tt Score-P} is a fully-featured profiler with some CUDA and OpenACC
support.  It can be useful for providing context for GPU execution and it allows
you to, for example, see line numbers for OpenACC directives that are executed.
{\tt nvprof} will only analyze GPU execution, but in exchange you get much more
detail than is available with {\tt Score-P}.  {\tt nvvp} is NVIDIA's visual
profiler.  It can be used to read data generated by {\tt nvprof}.  Most useful
is the guided analysis it will perform, which analyzes your code's GPU
performance for bottlenecks and suggests ways to improve performance.  Both are
provided when you load the {\tt cudatoolkit} module.

With {\tt nvprof}, no instrumentation is necessary.  Instead, you compile
normally and then run {\tt nvprof} on the executable.  As before, be sure when
executing to load the modules used at compile-time.  Executing {\tt nvprof} on
Titan's compute nodes requires some unexpected options having to do with how
{\tt aprun} and {\tt nvprof} interact.

@@

To generate tracing data for {\tt nvvp}, execute
\begin{lstlisting}[language=bash,mathescape=false]
$ aprun -b nvprof --profile-child-processes -o nvprof.timeline.out%p 
  ./gpuprogram.exe arg1 arg2... 
\end{lstlisting}
{\tt nvvp} can then be used to read {\tt nvprof.timeline.out\%p}, where the 
{\tt \%p} will be replaced with the process ID.  You \emph{must} include \%p in
the output file's name or the code will crash, even if you're not running a
multi-process code.
